Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows

### 2017-03-01 paper.tex
add more ignored files, fix figure

Restricting the allowed precursor masses is beneficial in searches that are intended to discover mass shift peaks. We ran a completely open precursor mass search, and restricted ourselves to looking at 1\% FDR matches, both targets and decoys. The plots in Figure~\ref{fgr:figure2-upperlowerbounds} show the FDR in the list filtered by using a lower or upper bound cutoff on the allowed mass shifts. It shows the fundamental difference between upper and lower bound cutoffs: while it is beneficial to restrict open searches to ignore large negative values, restricting matches with a large positive mass difference has a negative effect on the overall FDR.

>>>>

Restricting the allowed precursor masses is beneficial in searches that are intended to discover mass shift peaks. We ran a completely open precursor mass search, and restricted ourselves to looking at 1\% FDR matches, both targets and decoys. The plots in Figure~\ref{fig:figure2-upperlowerbounds} show the FDR in the list filtered by using a lower or upper bound cutoff on the allowed mass shifts. It shows the fundamental difference between upper and lower bound cutoffs: while it is beneficial to restrict open searches to ignore large negative values, restricting matches with a large positive mass difference has a negative effect on the overall FDR.
